Ideen zum Matching

### 2008-05-31 Algebras/RegionInterpolation/Tex/Quelltexte.tex
*** empty log message ***

\chapter{Quelltexte}
\minitoc
\newpage
\begin{landscape}
\section{ConvexHullTreeNode}
\begin{tiny}
\lstinputlisting[multicols=2,numbers=none]{ConvexHullTreeNode.java}
\end{tiny}
\end{landscape}

>>>>

\chapter{Quelltexte}
\minitoc
\newpage
\begin{landscape}

\begin{tiny}
\section{RegionInterpolator}
\lstinputlisting[language=c++,multicols=2,numbers=none]{RegionInterpolator.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{RegionInterpolator.cpp}
\section{Lines}
\lstinputlisting[language=c++,multicols=2,numbers=none]{Lines.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{Lines.cpp}
\section{ConvexHullTreeNode}
\lstinputlisting[language=c++,multicols=2,numbers=none]{ConvexHullTreeNode.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{ConvexHullTreeNode.cpp}
\section{Face}
\lstinputlisting[language=c++,multicols=2,numbers=none]{Face.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{Face.cpp}
\section{Region}
\lstinputlisting[language=c++,multicols=2,numbers=none]{Region.h }
\lstinputlisting[language=c++,multicols=2,numbers=none]{Region.cpp }
\section{RegionTreeNode}
\lstinputlisting[language=c++,multicols=2,numbers=none]{RegionTreeNode.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{RegionTreeNode.cpp}
\section{SingleMatch}
\lstinputlisting[language=c++,multicols=2,numbers=none]{SingleMatch.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{SingleMatch.cpp}
\section{Match}
\lstinputlisting[language=c++,multicols=2,numbers=none]{Match.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{Match.cpp}
\section{CentroidMatch}
\lstinputlisting[language=c++,multicols=2,numbers=none]{CentroidMatch.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{CentroidMatch.cpp}
\section{SteinerPointMatch}
\lstinputlisting[language=c++,multicols=2,numbers=none]{SteinerPointMatch.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{SteinerPointMatch.cpp}
\section{OverlapingMatch}
\lstinputlisting[language=c++,multicols=2,numbers=none]{OverlapingMatch.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{OverlapingMatch.cpp}
\section{OptimalMatch}
\lstinputlisting[language=c++,multicols=2,numbers=none]{OptimalMatch.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{OptimalMatch.cpp}
\section{mLineRep}
\lstinputlisting[language=c++,multicols=2,numbers=none]{mLineRep.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{mLineRep.cpp}
\section{Utils}
\lstinputlisting[language=c++,multicols=2,numbers=none]{Utils.h}
\lstinputlisting[language=c++,multicols=2,numbers=none]{Utils.cpp}
\end{tiny}
\end{landscape}
